---
title: "WFDS Alaska"
author: "Justin Ziegler"
date: "10/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(spatstat)
library(segmented)

results = as_tibble(expand.grid(
  state = c('1x','3x'),
  fuels = c('meanfuel','hifuel'),
  wx = c('hiwx','modwx'))) %>%
  mutate(treelist = list(rep(NA,8)),
         bndry = list(rep(NA,8)),
         sim= paste(state,fuels,wx,sep = '_'))

#results = filter(results, 
#                 !(sim == '1x_hifuel_hiwx'|
#                   sim == '1x_hifuel_modwx'))

headfolder = '/Users/katherinehayes/Library/CloudStorage/GoogleDrive-k8rhayes@gmail.com/My Drive/Projects/Reburns/Chapters/Flammabllity/data/fire behavior/results/wfdsresults/'


for (i in 1:nrow(results)){
  #Read in tracked trees
  ifolder = paste0(headfolder,'/',results$sim[i])
  results$treelist[[i]] = read_csv(paste0(ifolder,"/treelist.csv"),
                                   show_col_types = FALSE) %>% 
    separate(tree,sep = '_tree',into=c(NA,'tree')) %>%
    separate(tree,into='tree')
  
  #Extract characteristics of tracked trees
 ifile = read_delim(list.files(ifolder,
                               pattern = 'burn.txt',
                               full.names = TRUE)[1],
                    delim='/n')

  names(ifile) = 'col'

  #Calculate tracked tree crown consumption
  results$treelist[[i]] = left_join(
    filter(ifile, str_detect(col, 'OUTPUT_TREE=.TRUE.'))  %>%
    separate(col, sep = '=', 
             into =c(NA,'xyz','spp',NA,'cw','cbh','ht',NA,'id')) %>%
    separate(xyz, into =c('x','y')) %>%
    separate(spp, into =c(NA,'spp')) %>%
    separate(cw, into =c('cw'),sep = ',') %>%
    separate(cbh, into =c('cbh'),sep = ',') %>%
    separate(ht, into =c('ht'),sep = ',') %>%
    separate(id, into =c(NA,'id'),sep = 'tree') %>%
    separate(id, into =c('id')) %>%
    rename(tree=id), 
    results$treelist[[i]]) %>% 
    mutate(cc = 1-minfuel/maxfuel,  
           x = as.numeric(x),
           y = as.numeric(y),
           x = x - 360)
  
  #Pull in all trees - tracked and nontracked
  results$fulltreelist[[i]] = 
    filter(ifile, str_detect(col, "&TREE")) %>%
    separate(col, sep = '=',
             into =c(NA,'xyz','spp',NA,'cw','cbh','ht')) %>%
    separate(xyz, into =c('x','y')) %>%
    separate(spp, into =c(NA,'spp')) %>%
    separate(cw, into =c('cw'),sep = ',') %>%
    separate(cbh, into =c('cbh'),sep = ',') %>%
    separate(ht, into =c('ht'),sep = ',') %>%
    mutate(x = as.numeric(x) -360,
           y = as.numeric(y),
           cw = as.numeric(cw),
           cbh = as.numeric(cbh),
           ht = as.numeric(ht),
           vol = ifelse(spp=='PIME',pi*(cw/2)^2*ht/3,pi*(cw/2)^2*ht),
           mass = ifelse(spp=='PIME',vol*.5,vol*.2))
  
  #Make map of crown mass
  results$fulltreelistmap[[i]] = with(
    results$fulltreelist[[i]],
    ppp(x,y,c(-350,200),c(25,95),marks = mass)) %>%
    Smooth(eps=1) %>% 
    as_tibble() %>%
    rename(mass = value)
  
  #Read in surface fuels
  results$surffuel[[i]] = full_join(
    filter(ifile, str_detect(col, ",0,0,SURF_ID='bare' /")) %>%
      separate(col, sep="=", into =c(NA,'surf')) %>%
      separate(surf, into=c('x',NA,'y')) %>%
       mutate(class='bare',
              x = as.numeric(x),
              y = as.numeric(y)),
    expand.grid(x = 360:559,y=25:94)) %>%
    mutate(class = replace_na(class,'fuel'),
           load = case_when(
             results$state[[i]]=='1x' & class == 'fuel' ~ .1108,
             results$state[[i]]=='3x' & class == 'fuel' ~ .0373,
             class == 'bare' ~ .044),
             x = x-360)
  
  #Read in wind
  results$wind[[i]] = 
    bind_cols(
      bind_rows(
        read_csv(paste0(ifolder,'/wind8.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind9.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind10.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind11.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind12.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind13.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind14.csv'),col_names = FALSE)),
      bind_rows(
        read_csv(paste0(ifolder,'/wind15.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind16.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind17.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind18.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind19.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind20.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind21.csv'),col_names = FALSE)),
      bind_rows(
        read_csv(paste0(ifolder,'/wind22.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind23.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind24.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind25.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind26.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind27.csv'),col_names = FALSE),
        read_csv(paste0(ifolder,'/wind28.csv'),col_names = FALSE))) %>%
    mutate(y = paste0('y',1:147)) %>%
    pivot_longer(!y) %>% 
    mutate(x=rep(1:603,147)) %>%
    dplyr::select(-name) %>%
    separate(y, into=c(NA,'y'),sep='y') %>%
    mutate(y = as.numeric(y),
           y = 25 + 70*y/147,
           x = (260 + 300*x/603)-360) %>%
    rename(windspd = value)
  
  #Read in time of arrival
  results$bndry[[i]] = bind_rows(
    read_csv(paste0(ifolder,'/TOAbndry1.csv'),col_names = FALSE),
    read_csv(paste0(ifolder,'/TOAbndry2.csv'),col_names = FALSE)) 
  
  names(results$bndry[[i]]) = paste0('y',1:ncol(results$bndry[[i]]))
  
  results$bndry[[i]] = mutate(results$bndry[[i]],
                              x = paste0('x',1:nrow(results$bndry_pre[[i]]))) %>%
    pivot_longer(!x) %>%
    separate(x,sep='x',into=c(NA,'x')) %>%
    separate(name,sep='y',into=c(NA,'y')) %>%
    mutate(x = as.numeric(x)/2,y = as.numeric(y)/2) %>%
    rename(toa = value)
  
  #Simplify TOA cell 
   results$ros[[i]] = tibble(
    x=1:200,
    toa = predict(loess(toa~x,results$bndry[[i]],span = 0.75),
                  newdata = tibble(x=1:200)),
    ros = 1/(toa - lag(toa)))
}
  




results$segmentcc = 
  list(lm(cc ~ x, data=results$treelist[[1]]),
       segmented(lm(cc ~ x, data=results$treelist[[2]]), seg.Z = ~x, psi=c(15,35),npsi=2),
       segmented(lm(cc ~ x, data=results$treelist[[3]]), seg.Z = ~x, psi=c(20,40,60),npsi=3),
       segmented(lm(cc ~ x, data=results$treelist[[4]]), seg.Z = ~x, psi=c(10,30),npsi=2),
       segmented(lm(cc ~ x, data=results$treelist[[5]]), seg.Z = ~x, psi=c(30,50),npsi=2),
       segmented(lm(cc ~ x, data=results$treelist[[6]]), seg.Z = ~x, psi=c(18,25),npsi=2),
       segmented(lm(cc ~ x, data=results$treelist[[7]]), seg.Z = ~x, psi=c(15,34),npsi=2),
       segmented(lm(cc ~ x, data=results$treelist[[8]]), seg.Z = ~x, psi=c(18,30),npsi=2)
       )

results$segmentpredict = list(
  tibble(x=0:160,
         cc = predict(results$segmentcc[[1]],newdata = tibble(x=0:160))),
  tibble(x=0:160,
         cc = predict(results$segmentcc[[2]],newdata = tibble(x=0:160))),
  tibble(x=0:160,
         cc = predict(results$segmentcc[[3]],newdata = tibble(x=0:160))),
  tibble(x=0:160,
         cc = predict(results$segmentcc[[4]],newdata = tibble(x=0:160))),
  tibble(x=0:160,
         cc = predict(results$segmentcc[[5]],newdata = tibble(x=0:160))),
  tibble(x=0:160,
         cc = predict(results$segmentcc[[6]],newdata = tibble(x=0:160))),
  tibble(x=0:160,
         cc = predict(results$segmentcc[[7]],newdata = tibble(x=0:160))),
  tibble(x=0:160,
         cc = predict(results$segmentcc[[8]],newdata = tibble(x=0:160))))
for (i in 1:8){
  results$segmentpredict[[i]] = mutate(results$segmentpredict[[i]],
                                  cc = ifelse(cc>1,1,cc))} 
```

## Design

Complete balanced design with:

-   1x and 3x burned

-   Mean canopy fuels and high canopy fuels

-   Extreme burning conditions and moderate burning conditions

## Wind

```{r}
dplyr::select(results, sim, wind) %>% unnest() %>%
   ggplot(aes(x,y,fill=windspd)) + geom_raster() + coord_equal() +
    scale_fill_viridis_c(option='mako') +
  facet_wrap(~sim)+
  labs(x = 'X, distance from transition (m)', y = 'Y (m)')
    

dplyr::select(results, sim, wind) %>% unnest() %>%
  group_by(sim,x) %>% summarise(windspd = mean(windspd)) %>%
   ggplot(aes(x,windspd)) + geom_point() +
  facet_wrap(~sim) +
  labs(x = 'X, distance from transition (m)', y = 'Wind speed (m/s)')
    
  
```

## Surface fuels

```{r fuels, include=FALSE }


group_by(results,state) %>% filter(row_number()==1) %>%
dplyr::select(state,surffuel) %>% unnest() %>%
  ggplot(aes(x,y,fill=class)) +
  geom_raster() +
  theme_minimal() +
  coord_equal() +
  facet_wrap(~state)  +
  scale_fill_manual('Surface fuel class', 
                    values = c(topo.colors(10)[10],'forest green'),
                    labels =c('Litter only','Litter, Herb, Shrub'))+
   theme(legend.position='bottom') +
  labs(x = 'X, distance from transition (m)', y = 'Y (m)')
```

## Canopy Fuels

```{r canfuels, include=FALSE }

dplyr::select(results,sim,fulltreelist) %>% unnest() %>%
  group_by(sim) %>%
  filter(x>=0) %>%
  summarise(fuelload = sum(mass)/(70*200),
            fueldensity = sum(mass)/(70*200*quantile(ht,.9))
            )

#Doesn';t look okay.
#Canopy fuel gradient capped at X kg/m2
dplyr::select(results,sim,fulltreelistmap) %>% unnest() %>%
  filter(x>=0) %>% rowwise %>%
  ggplot(aes(x,y,z=mass)) +
  geom_contour(binwidth = .05) +
  theme_minimal() +
  coord_equal() +
  facet_wrap(~sim) +
   theme(legend.position='bottom') +
  labs(x = 'X, distance from transition (m)', y = 'Y (m)')
```

## Tree Consumption

You can also embed plots, for example:

```{r pressure, include=FALSE}
dplyr::select(results,sim,treelist) %>% unnest() %>%
  ggplot(aes(x,y,fill = cc, size = maxfuel)) +
  geom_point(pch=21) +
  coord_equal(expand=FALSE) +
  facet_wrap(~sim) +
  scale_fill_viridis_b(option = 'B') +
  theme_minimal()
  


dplyr::select(results,sim,treelist) %>% unnest() %>%
  ggplot(aes(x,cc, size = maxfuel)) +
  geom_point(pch=21) +
  coord_cartesian(expand = FALSE)  +
  theme_minimal()+
  facet_wrap(~sim) +
  geom_line(
    data = dplyr::select(results,sim,segmentpredict) %>% unnest(),
    lwd = 1,
    col='blue'
  )


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Time of Arrival

```{r, include=FALSE}

group_by(results,sim) %>% filter(row_number()==1) %>%
dplyr::select(state,surffuel) %>% unnest() %>%
  ggplot(aes(x,y,fill=class)) +
  geom_raster() +
  theme_minimal() +
  coord_equal(expand=FALSE) +
  facet_wrap(~sim)  +
  scale_fill_manual('Surface fuel class', 
                    values = c(topo.colors(10)[10],'forest green'),
                    labels =c('Litter only','Litter, Herb, Shrub'))+
   theme(legend.position='bottom') +
  labs(x = 'X, distance from transition (m)', y = 'Y (m)') +
  geom_raster(data = dplyr::select(results, sim, bndry) %>% unnest() %>% na.omit(),
    aes(x,y+25,z = toa), 
    inherit.aes = FALSE) +
  geom_contour(
    data = dplyr::select(results, sim, bndry) %>% unnest(),
    aes(x,y+25,z = toa),
    binwidth = 10000, 
    inherit.aes = FALSE
  ) +
  geom_contour(
    data = dplyr::select(results, sim, bndry) %>% unnest() %>% group_by(sim),
    aes(x,y+25,z = toa),
    binwidth = 10, 
    inherit.aes = FALSE
  )


```

## Rate of Spread

```{r, include=FALSE}

dplyr::select(results, sim, ros) %>% unnest() %>%
  ggplot(aes(x,ros)) +
  geom_line()  +
  theme_minimal() +
  facet_wrap(~sim)  +
  labs(x = 'X, distance from transition (m)', y = 'Rate of Spread (m/s)')


  
```
